--- 
title: "Data Cafe Dashboard"
author: "Dianara Sagastizado"
format: dashboard
params:
  month: "November 4"
  year: "2024"
---

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
```

```{r}
#| label: set-inputs

time_period <- paste(params$month, params$year)
```

#   {.sidebar}

Data Cafe tutor schedule as of `{r} time_period`:

| 4-5pm    |                         |
|----------|-------------------------|
| Sunday   | **Thoan Nguyen**        |
| Monday   | **Dianara Sagastizado** | 
| Tuesday  | **Tova Benson**         |
| Wednesday| **Thoan Nguyen**        | 
| Thursday | **Thoan Nguyen**        |
| Friday   | **Tova Benson**         |


| 8-9pm    |                         |
|----------|-------------------------|
| Sunday   | **Maggie Giardello**    |
| Monday   | **Maggie Giardello**    | 
| Tuesday  | **Isabella Moore**      |
| Wednesday| **Tova Benson**         | 
| Thursday | **Isabella Moore**      |
| Friday   | **Dianara Sagastizado** |


## Row {height=30%}

```{r}
#| label: popular-date-and-time
#| title: "Popular day of the week and time"
```

```{r}
#| label: visitors-this-week
#| title: "Visitors this week"
```

```{r}
#| label: popular-course-this-week
#| title: "Popular course"
```

## Row {.tabset}

```{r}
#| label: weeky-popular-shifts
#| title: "Popular shift throughout the week"

```

```{r}
#| label: students-over-time
#| title: "Students attending data cafe throughout semester"
```

```{r}
#|label: course-frequency
#|title: "Course frequencies throughout semester"
```
